The Werewolf Among Us: Humans vs LLMs in Multi-Agent Games

### 2025-05-07 Quarto/paper.qmd
Update Intro, Methods, WWA GUI Figure

Agents participated in gameplay through a graphical user interface (GUI), depicted in Figure 1. The GUI displays the game state, including player roles, actions, and current discussion rounds, enabling monitoring of the gameplay progression.

@@

![GUI of Werewolf Arena simulation](Images/WWA_GUI.PNG.png)

>>>>

Agents participated in gameplay through a graphical user interface (GUI), depicted in Figure @fig-wwa-gui. The GUI displays the game state, including player roles, actions, and current discussion rounds, enabling monitoring of the gameplay progression.

@@

![GUI of Werewolf Arena simulation](Images/WWA_GUI.png){#fig-wwa-gui}
